Variable creation ObjectInAction

### 2020-06-22 Final_Manuscript.Rmd
change author order, affiliation

author: 
  - name          : "Kat Kyuchukova"
    affiliation   : "1"
  - name          : "Asha Hinson"
    affiliation   : "1"
  - name          : "Randi L. Garcia"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Smith College"

@@

#Introduction
Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences and therefore inform individuals’ thinking, feeling, and behavior, especially during interpersonal interactions with members of different social groups [@Kaschak]. Empirical evidence illustrates how women, in particular,  continue to be objects of perpetual discrimination as a result of psychosocial markers, like gender, that produce modes through which their identity is understood [@swimetal]. Objectification theory, a valuable theoretical framework proposed by @robertsfredrickson which works to contextualize female bodies as socio-cultural constructions, can be employed to illuminate the gender oppression and negative lived experiences of girls and women.

>>>>

author: 
  - name          : "Randi L. Garcia"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "415 Bass Hall, Smith College, Northampton, MA 01060"
    email         : "rgarcia@smith.edu"
  - name          : "Kat Kyuchukova"
    affiliation   : "1"
  - name          : "Asha Hinson"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Smith College"
  - id            : "2"
    institution   : "Program in Statistical and Data Sciences, Smith College"

@@

Theorists across diverse disciplines have explored the multiple ways that the body conveys social meaning, as well as how these meanings shape gendered experiences and therefore inform individuals’ thinking, feeling, and behavior, especially during interpersonal interactions with members of different social groups [@Kaschak]. Empirical evidence illustrates how women, in particular,  continue to be objects of perpetual discrimination as a result of psychosocial markers, like gender, that produce modes through which their identity is understood [@swimetal]. Objectification theory, a valuable theoretical framework proposed by @robertsfredrickson which works to contextualize female bodies as socio-cultural constructions, can be employed to illuminate the gender oppression and negative lived experiences of girls and women.
